### 2012-05-23 inst/examples/policycosts/exact_npv.Rmd

``` {r setup, include=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
````

@@

``` {r npv-plot}
npv0 <- dat[1,3] 
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

@@

```{r comparison}
dat <- data.table(dat)
int <- dat[,findInterval(.75*npv0, (npv0-value)/value), by="variable"]$V1
dat$c2[int]
````

>>>>

``` {r setup, include=FALSE }
#opts_knit$set(upload.fun = socialR::flickr.url)
````

@@

``` {r npv-plot}
npv0 <- dat[1,3] 
npv0
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

@@

```{r comparison}
closest <- function(x, v){
	which.min(abs(v-x))
}

ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/value), by=variable]
cbind(index, c2=c2[index$V1])
````
